Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-11 main_paper.tex
Add references to other papers in the volume
As Matias requested (possibly in person), I've added references to other
related papers in the volume to our introduction.

The RD design strategy was introduced by \cite{thistlethwaite1960} to study
educational outcomes and many of its recent applications in economics were to
estimate the effects of other educational policies: evaluating the impact of
investments in school facilities, class sizes, remedial education, early
childhood education, and financial aid effects on student achievement and
later outcomes, for example.\footnote{%
  See, for example, \cite{vdk2002}, \cite{jacoblefgren2004},
  \cite{ludwig2007}, \cite{urquiola2009}, \cite{cellini2010}} %
But the underlying identification strategy has proven to apply much more
widely and RD has been used in health economics,\footnote{%
  \cite{Card2009,barreca2011saving}} %
political science,\footnote{%
  \cite{lee2008}, \cite{caughey2011elections}, \cite{keele2014geographic},
  \cite{erikson2015}, \cite{Fujiwara2011,Fujiwara2015}} %
and labor economics,\footnote{%
  \cite{schmieder2012}.} %
among other fields. \cite{imbens2008} and \cite{lee2010} provide recent
overviews of this literature with many more examples.

@@

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodated in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and one limitation should be noted in particular. The confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Moreover, in this paper we focus on the baseline case of
sharp RD with a local linear model, however, the results and procedures can be easily extended to the general local polynomial
and higher order derivatives cases (e.g., Regression Kink Designs).

@@

For this model, if $h$ represents a bandwidth parameter and $K(\cdot)$ a density
function, the estimator of $\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  \hat {\mu}_{+}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h}K(X_{i}/h)
\intertext{and}
  \hat {\mu}_{-}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h} K_{h}(X_{i}/h).
\end{align*}

Conventional (naive) confidence intervals can be calculated by using an
asymptotic approximation for $\hat\tau(h)$. In particular, if
\begin{gather}
  \label{eq:1}
  \frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
  \intertext{with}
  \notag
  V(h) \big/ \V(\hat\tau(h) \mid X_{1},\dots,X_{n}) \to^p 1
\end{gather}
then valid confidence intervals can be constructed through the usual method of
inverting the $t$-test.\footnote{%
  The mathematical appendix of this paper gives a precise definition for
  $V(h)$.} %
This procedure gives the widely-used interval estimator
\begin{equation*}
  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
\end{equation*}
where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
distribution.

@@

\begin{assumption}[Bandwidth and kernel]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}
  The kernel function $K$ is positive and continuous on the interval
  $[-\kappa,~\kappa]$ and zero outside that interval.
\end{assumption}
To simplify notation, define the scaled kernel functions
\begin{align*}
  K_h(x) &= \tfrac{1}{h} K(x/h)
\intertext{and}
  K_b(x) &= \tfrac{1}{b} K(x/b).
\end{align*}
Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
in practice.  Note that different kernel functions could be used for the
treatment effect estimator and the higher order approximation used for the
bootstrap.  For simplicity, though, we use the same function for all steps of
estimation in this paper.  Potentially different kernel functions and bandwidths
could also be used for estimation below and above the cutoff, but we again focus
on the simpler case here.

@@

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
\end{theorem}

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define the same notation as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate $\hat{g}_{+}$ and $\hat{g}_{-}$ and generate $\hat g(\cdot)$
    and the residuals $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.
  \item Repeat the following steps $B_{2}$ times to produce the
    bootstrap estimates
    $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw i.i.d.\ random variables $e_i^{*}$ with mean zero, variance one,
      and bounded fourth moments independent of the original data and
      construct
      \begin{align*}
        \varepsilon_i^{*} &= \hat{\varepsilon}_i e^{*}_i,
        \intertext{and}
        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{-}}
          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{h}(X_{i}) \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{+}}
          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{h}(X_{i}).
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set
      using the same bandwidths $h$ and $b$ that are used in the rest of this
      algorithm but reestimating all of the local polynomials on the bootstrap
      data. Generate $B_1$ new bootstrap samples and let $\Delta^{**}(h,b)$
      represent the bias estimator returned by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
      - \Delta^{**}(h,b)$.
    \end{enumerate}
  \item Use the empirical CDF of
    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
    construct confidence intervals, etc.
  \end{enumerate}
\end{algorithm}

@@

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1} and~\ref{A2},
  \begin{gather*}
    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
  \intertext{and}
    \sup_{x}
    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
  \end{gather*}
\end{theorem}

@@

\section{Simulation Evidence}\label{sim}

This section presents evidence from Monte Carlo simulations that the bootstrap
procedures proposed in Section~\ref{boot} produce valid, robust confidence
intervals similar to those obtained by the analytical procedures established
in CCT. The bootstrap CIs obtained compare favorably to the analytical
alternative, with coverage slightly closer to nominal coverage and shorter
length of the intervals in the specifications implemented. We also find that
all of the bias corrected methods can offer substantial improvements over
estimators that do not bias correct, including a ``naive'' bootstrap procedure.

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim N(0, \sigma_i^2) \\
\sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
\end{align*}
where $j$ will index the specific DGP. This is the experimental design used by
\citet{IK} and CCT, which we adopt here with adaptation to make our simulation results directly
comparable with theirs and with the rest of the literature. They use this experimental design with a constant $\sigma_i = 0.1295$. We follow \cite{mackinnon2013thirty} to use a parameter $\gamma$ and a function $z(\gamma)$ to control the degree of heteroskedasticity. When $\gamma = 0$, we set $z(\gamma) = 0.1295$ such that our DGP is exactly the same as \citet{IK} and CCT. When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.
\footnote{The rescaling requires that $\max(h, b)$ is known, which is usually not the case in practice because $h$ and $b$ are data-driven. For simplicity, we firstly find $\overline{\max[h, b]}$ from \textbf{homoskedastic} data through 500 replications and then calculate $z(\gamma)$ for every bootstrap data accordingly. In our simulation, $\overline{\max[h, b]}$ is obtained by (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector and (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$. Once $\overline{\max[h, b]}$ is known, we use it to generate heteroskedastic data using following steps: (1) generate random running variable $X_i$, (2) let $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$ and calculate the standard deviation and (3) generate disturbance term and outcome $Y_i$ accordingly.} 
We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.

\nocite{lee2008rand}%
The first DGP is designed to match features of Lee's (2008) analysis of U.S.\
congressional elections. Lee estimates the incumbency advantage in electoral
races for the House of Representatives --- candidates who received the largest
vote share in the previous election are the incumbents, which creates the
discontinuity. The conditional expectation is a fifth order polynomial fit to
that dataset, (after excluding a small number of extreme observations; see
\citealp{IK}, or CCT for further details) giving
\begin{equation*}
  \mu_{1}(x) =
  \begin{cases}
    0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}
    & \textif\ x < 0 \\
    0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5}
    & \otherwise.
  \end{cases}
\end{equation*}
The population ATE for this DGP is $0.04$ $(= 0.52 - 0.48)$.

@@

Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
``Wild bootstrap'' shows results for our proposed bootstrap interval and ``CCT'' shows
results for the analytically-corrected interval. The first three columns give the bias,
standard deviation, and Root-MSE of the point
estimators corresponding to each confidence interval.  As expected, both
bias corrected estimators have
bias close to zero, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.

The column ``CI Coverage'' lists the experimental coverage of each interval.
In Panel A, all of the intervals from both robust estimators are reasonably close to their nominal coverage, although
our proposed bootstrap procedure has coverages about one percentage lower than the CCT's analytical counterpart. In Panel B, the coverages are very similar to those in Panel A, showing that both procedures are robust to heteroskedasticity. 
The final column, ``CI Length,'' 
indicates that our proposed bootstrap procedure consistently generates narrower intervals.

These are DGPs where the naive confidence intervals are known to perform poorly,
and this set of simulation results indicates that our proposed bootstrap approach
is quite competitive with analytical methods for producing valid intervals.
Overall, the bootstrap bias-correction procedure proposed in this paper provides
a simple alternative to obtain valid robust confidence intervals in RD designs
and performs well compared to the analytical bias correction procedures proposed
by CCT.

@@

\begin{table}[t]
  \centering
  \begin{tabular}{lrr@{, }rr@{}rrr}
    \toprule
                      & ATE     & \multicolumn{2}{r}{95\% CI}            &     &  $h$ &   $b$ & p-value \\
    \midrule
    LM (2007)         & --1.895 & (--3.930                    & 0.139)   & 9   &      &       & 0.036 \\
    LM (2007)         & --1.198 & (--2.561                    & 0.165)   & 18  &      &       & 0.081 \\
    LM (2007)         & --1.114 & (--2.138                    & --0.090) & 36  &      &       & 0.027 \\
    CCT               & --3.795 & (--6.885                    & --0.706) & 3   & .888 & 6.807 &       \\ 
    Wild bootstrap    & --3.800 & (--6.781                    & --0.408) & 3   & .888 & 6.807 &       \\
    \bottomrule
  \end{tabular}
  \caption{The effect of Head Start assistance on mortality. The first three
    rows come from Table 3 in \cite{ludwig2007} except ``95\% CI,'' which is
    calculated using the conventional asymptotic interval estimator.
    The last two rows list results from two robust procedures.}
  \label{tbl:2}
\end{table}

@@

The two robust procedures are again very similar to each other and give slightly
larger point estimates in both panels. In Panel A, the ATE increases from 0.030
to 0.055 (CCT and bootstrap). In Panel B, the ATE increases from 0.037
to 0.051 (CCT) and 0.052 (bootstrap). The confidence intervals tend to shift up
as well.  In contrast to the striking differences between the conventional
estimates bias-corrected procedures for the mortality estimates, the differences
in Table~\ref{tbl:3} are much smaller.

>>>>

The RD design strategy was introduced by \cite{thistlethwaite1960} to study
educational outcomes and many of its recent applications in economics were to
estimate the effects of other educational policies: evaluating the impact of
investments in school facilities, class sizes, remedial education, early
childhood education, and financial aid effects on student achievement and
later outcomes, for example.\footnote{%
  See, for example, \cite{vdk2002}, \cite{jacoblefgren2004},
  \cite{ludwig2007}, \cite{urquiola2009}, and \cite{cellini2010}.} %
But the underlying identification strategy has proven to apply much more
widely and RD has been used in health economics,\footnote{%
  \cite{Card2009}, \cite{barreca2011saving}, and \cite{KeeleEtAl}.} %
political science,\footnote{%
  \cite{lee2008}, \cite{caughey2011elections}, \cite{keele2014geographic},
  \cite{erikson2015}, and \cite{Fujiwara2011,Fujiwara2015}.} %
and labor economics,\footnote{%
  \cite{schmieder2012} and \cite{frandsen}.} %
among other fields. \cite{imbens2008} and \cite{lee2010} provide recent
overviews of this literature with many more examples.

@@

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodated in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and one limitation should be noted in particular. The confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Moreover, in this paper we focus on the baseline case of
sharp RD with a local linear model, however, the results and procedures can be
easily extended to the general local polynomial and higher order derivatives
cases (e.g., Regression Kink Designs, see \citealp{CardEtAl1,CardEtAl2}).

@@

For this model, if $h$ represents a bandwidth parameter and $K(\cdot)$ a density
function, the estimator of $\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  \hat {\mu}_{+}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h}K(X_{i}/h)
\intertext{and}
  \hat {\mu}_{-}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h} K(X_{i}/h).
\end{align*}

Conventional (naive) confidence intervals can be calculated by using an
asymptotic approximation for $\hat\tau(h)$. In particular, if
\begin{gather}
  \label{eq:1}
  \frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
  \intertext{with}
  \notag
  V(h) = \V(\hat\tau(h) \mid X_{1},\dots,X_{n}),
\end{gather}
then valid confidence intervals can be constructed through the usual method of
inverting the $t$-test.\footnote{%
  The mathematical appendix of this paper gives a precise definition for
  $V(h)$.} %
This procedure gives the widely-used interval estimator
\begin{equation*}
  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
\end{equation*}
where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
distribution.

@@

\begin{assumption}[Bandwidth and kernel]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}
  The kernel function $K$ is positive and continuous on the interval
  $[-\kappa,~\kappa]$ and zero outside that interval.
\end{assumption}
To simplify notation, let $m = \min(h,b)$, $m' = \max(h,b)$, and
define the scaled and truncated kernel functions
\begin{align*}
  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \geq 0\} &
  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x < 0\}
\intertext{and}
  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \geq 0\} &
  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x < 0\}.
\end{align*}
Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
in practice. Note that different kernel functions could be used for the
treatment effect estimator and the higher order approximation used for the
bootstrap.\footnote{%
  It would be a slight abuse of notation for $K_{+,h}$, $K_{-,h}$,
  $K_{+,b}$, and $K_{-,b}$ to all use different underlying kernels but
  would not affect our proofs.} %
For simplicity, however, we use the same function for all steps of
estimation in this paper.  Potentially different kernel functions and bandwidths
could also be used for estimation below and above the cutoff, but we again focus
on the simpler case here.

@@

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V^{bc}(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\eqref{eq:9}.
\end{theorem}

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and
  Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate $\hat{g}_{+}$ and $\hat{g}_{-}$ and generate $\hat g(\cdot)$
    and the residuals $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.
  \item Repeat the following steps $B_{2}$ times to produce the
    bootstrap estimates
    $\hat\tau_1^{bc*}(h,b), \dots, \hat\tau_{B_{2}}^{bc*}(h,b)$. For the
    $k$th replication:
    \begin{enumerate}
    \item Draw i.i.d.\ random variables $e_i^{*}$ with mean zero, variance one,
      and bounded fourth moments independent of the original data and
      construct
      \begin{align*}
        \varepsilon_i^{*} &= \hat{\varepsilon}_i e^{*}_i,
        \intertext{and}
        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}.
      \end{align*}
      for all $i = 1,\dots,n$.
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set using $K_{+,h}$ and $K_{-,h}$
      for weights:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i = 1}^n
          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{-,h}(X_{i}), \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i = 1}^n
          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{+,h}(X_{i}).
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set
      $(Y_1^*,\, X_1),\dots,(Y_n^*,\, X_n)$ set using the same bandwidths
      $h$ and $b$ that are used in the rest of this
      algorithm but reestimating all of the local polynomials on the bootstrap
      data. Generate $B_1$ new bootstrap samples and let $\Delta^{**}(h,b)$
      represent the bias estimator returned by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{bc*}(h,b) = \hat\mu_+^*(h) - \hat\mu_-^*(h)
      - \Delta^{**}(h,b)$.
    \end{enumerate}
  \item Define $\tau^* = \hat g_+(0) - \hat g_-(0)$ and use the empirical CDF of
    $\hat\tau_1^{bc*}(h,b) - \tau^*,\dots, \hat\tau_{B_2}^{bc*}(h,b) - \tau^*$
    as the sampling distribution of $\hat \tau^{bc} - \tau$.
  \end{enumerate}
\end{algorithm}

One brief remark on implementing these algorithms. Many of the matrix operations
required to estimate the local polynomials only involve the regressors and,
therefore, only need to be computed once. For example, the parameter estimates
for the linear model on the treated group are equal to
\[
\hat\beta_{+,1} = \underbrace{(\mathbf{X}' \mathbf{K}_+ \mathbf{X})^{-1} \mathbf{X}' \mathbf{K}_+}_{\mathbf{W}_{+,1}} \mathbf{Y}
\]
where
\begin{align*}
\mathbf{X} &= \begin{pmatrix*} 1 & X_1 \\ 1 & X_2 \\ \vdots & \vdots \\ 1 & X_n \end{pmatrix*} &
\mathbf{Y} &= \begin{pmatrix*} Y_1 \\ Y_2 \\ \vdots \\ Y_n \end{pmatrix*} &
\mathbf{K}_+ &= \begin{pmatrix*}
  K_{+,h}(X_1) & 0 & \cdots & 0 \\
  0 & K_{+,h}(X_2) & \cdots & 0 \\
  0 & 0 & \ddots & 0 \\
  0 & 0 & \cdots & K_{+,h}(X_n) \end{pmatrix*}.
\end{align*}
The matrix $\mathbf{W}_{+,1}$ is not affected by the bootstrap so it can be
computed once initially and reused in the bootstrap calculations and each
bootstrap replication just requires a single matrix-vector multiplication. The
other parameter estimates have this property as well. Consequently, the
computational burden of this iterated bootstrap is much lower than might
appear.\footnote{%
  An open-source implementation of this algorithm written in R, which was used
  for the empirical and Monte Carlo components of this paper, is available
  online at \url{https://github.com/grayclhn/boot-rd}.} %

@@

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1} and~\ref{A2},
  \begin{equation*}
    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V^{bc}(h,b) \to^p 1
  \end{equation*}
  and
  \begin{multline*}
    \sup_{x,\tau}
    \Big\rvert \Pr^*\big[ \sqrt{nh}
    (\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^*) \leq x \big] \\
    - \Pr\big[ \sqrt{nh}
    (\hat\tau(h) - \Delta^*(h,b) - \tau) \leq x \big] \Big\lvert \to^p 0.
  \end{multline*}
\end{theorem}

@@

\section{Simulation Evidence}\label{sim}
This section presents evidence from Monte Carlo simulations that the bootstrap
procedures proposed in Section~\ref{boot} produce valid, robust confidence
intervals similar to those obtained by the analytical procedures established
in CCT. The bootstrap CIs obtained are comparable to the analytical
alternative, albeit with slightly lower coverage and shorter
length of the intervals in the specifications implemented. We also find that
all of the bias corrected methods can offer substantial improvements over
estimators that do not bias correct.

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim N(0, \sigma_i^2) \\
\sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
\end{align*}
where $j$ will index the specific DGP. This is the experimental design used by
\citet{IK} and CCT, which we adopt here with adaptation to make our simulation results directly
comparable with theirs and with the rest of the literature. While they use this experimental design with homoskedastic errors, we introduce heteroskedasticity following the design in \cite{mackinnon2013thirty}. We control the degree of heteroskedasticity through the parameter $\gamma$ and a function $z(\gamma)$. When $\gamma = 0$, we set $z(\gamma) = 0.1295$ such that our DGP is exactly the same as \citet{IK} and CCT. When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.\footnote{In practice, the optimal $h$ and $b$ are usually data driven, so $h$, $b$ and $\sigma_i$ are simultaneously determined. For simplicity, we use the following steps to find $z(\gamma)$: (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector, (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$ and (3) define $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$.} We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.

\nocite{lee2008rand}%
The first DGP is designed to match features of Lee's (2008) analysis of U.S.\
congressional elections. Lee estimates the incumbency advantage in electoral
races for the House of Representatives --- parties that received the largest
vote share in the previous election are the incumbents, which creates the
discontinuity. The conditional expectation is a fifth order polynomial fit to
that dataset, (after excluding a small number of extreme observations; see
\citealp{IK}, or CCT for further details) giving
\begin{equation*}
  \mu_{1}(x) =
  \begin{cases}
    0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}
    & \textif\ x < 0 \\
    0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5}
    & \otherwise.
  \end{cases}
\end{equation*}
The population ATE for this DGP is $0.04$ $(= 0.52 - 0.48)$.

@@

Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
``Wild bootstrap'' shows results for our proposed bootstrap interval and ``CCT'' shows
results for the analytically-corrected interval. The first three columns give the bias,
standard deviation, and Root-MSE of the point
estimators corresponding to each approach.  As expected, both
bias corrected estimators have
bias close to zero, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.

The column ``CI Coverage'' lists the experimental coverage of each interval.
In Panel A, all of the intervals from both robust estimators are reasonably close to their nominal coverage, although
our proposed bootstrap procedure has coverages about one percentage lower than the CCT's analytical counterpart. In Panel B, the coverages are very similar to those in Panel A, showing that both procedures are robust to heteroskedasticity. 
The final column, ``CI Length,'' indicates that our proposed bootstrap procedure consistently generates narrower intervals, in line with the coverage results.

These are DGPs where the naive confidence intervals are known to perform poorly,
and this set of simulation results indicates that our proposed bootstrap approach
is quite competitive with analytical methods for producing valid intervals.
Overall, the bootstrap bias-correction procedure proposed in this paper provides
a simple alternative to obtain valid robust confidence intervals in RD designs
and similarly well compared to the analytical bias correction procedures proposed
by CCT.

@@

\begin{table}[t]
  \centering
  \begin{tabular}{lrr@{, }rr@{}rrr}
    \toprule
                      & ATE     & \multicolumn{2}{r}{95\% CI}            &     &  $h$ &   $b$ & p-value \\
    \midrule
    LM (2007)         & --1.895 & (--3.930                    & 0.139)   & 9   &      &       & 0.036 \\
    LM (2007)         & --1.198 & (--2.561                    & 0.165)   & 18  &      &       & 0.081 \\
    LM (2007)         & --1.114 & (--2.138                    & --0.090) & 36  &      &       & 0.027 \\
    CCT               & --3.795 & (--7.040                    & --0.551) & 3   & .888 & 6.807 &       \\ 
    Wild bootstrap    & --3.800 & (--6.738                    & --0.450) & 3   & .888 & 6.807 &       \\
    \bottomrule
  \end{tabular}
  \caption{The effect of Head Start assistance on mortality. The first three
    rows come from Table 3 in \cite{ludwig2007} except ``95\% CI,'' which is
    calculated using the conventional asymptotic interval estimator.
    The last two rows list results from two robust procedures.}
  \label{tbl:2}
\end{table}

@@

The two robust procedures are again very similar to each other and give slightly
larger point estimates in both panels. In Panel A, the ATE increases from 0.030
to 0.055 (CCT and bootstrap). In Panel B, the ATE increases from 0.037
to 0.051 (CCT) and 0.052 (bootstrap). The confidence intervals tend to shift up
as well.  In contrast to the striking differences between the conventional
and bias-corrected procedures for the mortality estimates, the differences
in Table~\ref{tbl:3} are much smaller.

\begin{table}[t]
  \centering
  \begin{tabular}{lrr@{, }rr@{}rrr}
    \toprule
                   & ATE   & \multicolumn{2}{r}{95\% CI} & & $h$     & $b$ & p-value     \\
    \midrule                                                                          \\
    \multicolumn{5}{l}{Fraction ``high school or more'' (Panel A)}                    \\
    \midrule
    LM (2007)      & 0.030 & (0.003                      & 0.057) & 7&     &  & 0.032    \\
    CCT            & 0.055 & (0.014                      & 0.096) & 3&.671 & 8.618       \\
    Wild bootstrap & 0.055 & (0.010                      & 0.096) & 3&.671 & 8.618       \\\\
    \multicolumn{5}{l}{Fraction ``some college or more'' (Panel B)}                   \\
    \midrule
    LM (2007)      & 0.037 & (0.002                      & 0.073) & 7&     &  & 0.032 \T \\
    CCT            & 0.051 & (0.004                      & 0.099) & 5&.076 & 10.251      \\
    Wild bootstrap & 0.052 & (0.007                      & 0.091) & 5&.076 & 10.251      \\
    \bottomrule
  \end{tabular}
  \caption{The effect of Head Start assistance on education for cohort
    18--24 in 1990. Panel A uses the fraction of people with high school
    or more as dependent variable. Panel B uses the fraction of people
    with some college or more as dependent variable. The first row in
    each panel comes from Table 4 in \cite{ludwig2007} except ``95\% CI,''
    which is calculated using the conventional asymptotic interval estimator.
    The last two rows in
    each panel list results from two robust procedures.}
  \label{tbl:3}
\end{table}
